The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-08 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

years <- 2010:2020
winpct <- c(.6707, .667, .679, .635, .562, .593, .6744, .5696, .707, .561, .482)
```

@@

(ref:cap-Fig1) "Winning percentage of NBA home teams in the playoffs since 2010, the green line denotes .500"
```{r Fig1, echo=FALSE, fig.cap = " (ref:cap-Fig1)", fig.align='center'}
winyear <- cbind(winpct, years)
winyear <- as.data.frame(winyear)
highlight <- data.frame(winpct = .482, years = 2020)
ggplot(winyear, aes(x=years, y=winpct))+ 
      geom_point()+
      geom_point(data=highlight, 
             aes(x=years, y=winpct), 
             color='red')+
      scale_x_continuous(name = "Year", breaks = years, labels = years)+
      scale_y_continuous(limits = c(0.4, 0.8))+
      geom_hline(aes(yintercept = 0.5), color = "green")+
      geom_text(aes(label=winpct), hjust=0, vjust=-1)
```

>>>>

years <- 2010:2020
winpct <- c(.671, .667, .679, .635, .562, .593, .674, .570, .707, .561, .482)
```

@@

(ref:cap-Fig1) "Winning percentage of NBA home teams in the playoffs since 2010, the green line denotes .500"
```{r Fig1, echo=FALSE, fig.cap = " (ref:cap-Fig1)", fig.align='center'}
winyear <- cbind(winpct, years)
winyear <- as.data.frame(winyear)
highlight <- data.frame(winpct = .482, years = 2020)
ggplot(winyear, aes(x=years, y=winpct))+ 
      geom_point()+
      geom_point(data=highlight, 
             aes(x=years, y=winpct), 
             color='red')+
      scale_x_continuous(name = "Year", breaks = years, labels = years)+
      scale_y_continuous(limits = c(0.4, 0.8))+
      geom_hline(aes(yintercept = 0.5), color = "green")+
      geom_text(aes(label=winpct), hjust=0, vjust=-1, size=2)
```
